---
title: "R package"
author: "Dr Wayne Stewart"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction



Congratulations for getting this far. To complete the evidence that you have made a working R package please answer the following by using the supplied rmd  and upload the knitted html to CANVAS.

I will assume your package is called **MYPAC** and you have packaged and documented functions `myf1`, `myf2`, `myf3` and `myf4`.

Your actual package name and functions will obviously be called something else.

# First function

Please place your first function in the r chunk in the following way:

Once you are ready please remove the option `eval = FALSE`

```{r first}

limb.counts = c(15, 8, 63, 20);
limb.labels = c("None", "Both", "Legs ONLY", "Wheels ONLY");
limb.freq.df = as.data.frame(matrix(data= limb.counts/sum(limb.counts), nrow=4, ncol=1), row.names = limb.labels);
limb.freq.df
limb.raw = rep(limb.labels, limb.counts);
PackageZuyus::pareto(x=limb.raw)

```


# Second function

Please place your second function in the r chunk in the following way:

Once you are ready please remove the option `eval = FALSE`

```{r second}

y=c(10,12,13,15,12,11,10)
PackageZuyus::mymlnorm(x=y,mu=seq(8,16,length=1000), sig=seq(0,4,length=1000), lwd=2,labcex=1)

```


# Third function

Please place your third function in the r chunk in the following way:

Once you are ready please remove the option `eval = FALSE`

```{r third}

set.seed(23);x = rnorm(30,mean=10,sd=12)
PackageZuyus::myci(x)

```


# Forth function

Please place your forth function in the r chunk in the following way:

Once you are ready please remove the option `eval = FALSE`

```{r forth}

PackageZuyus::mybin(iter=100, n=10, p=0.7)

```

# The github repository



This is the address of my GITHUB repository:
<https://github.com/marissazuyus/Stat_PackageZuyus.git>

Replace this with your own address.
